Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-07-13 manuscript/tables&figures.Rmd
minor figure file updates

\blandscape
```{r Table 1, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
hypothesis_table <- read.csv("tables_figures/publication/table1_hypothesis_table.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(hypothesis_table, format = "latex", booktabs = TRUE, caption = "Table 1. Summary of hypotheses, corresponding specific predictions, and results.") %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 8.5, protect_latex = TRUE) %>%
  pack_rows("Tree size and microenvironment", 1, 5, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("Taller trees have lower Rt.", 1, 1, latex_gap_space = "1em", colnum = 1, hline_before = FALSE, bold = FALSE, italic = TRUE) %>%
  pack_rows("Trees with more exposed crowns have lower Rt.", 2, 2, latex_gap_space = "1em", colnum = 1, hline_before = FALSE, bold = FALSE, italic = TRUE) %>%
  pack_rows("Small trees (lower root volume) in drier microhabitats have lower Rt.", 3, 3, latex_gap_space = "1em", colnum = 1, hline_before = FALSE, bold = FALSE, italic = TRUE) %>%
  pack_rows("Species traits", 4, 8, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("Species' traits--particularly leaf hydraulic traits--predict Rt.", 4, 8, latex_gap_space = "1em", colnum = 1, hline_before = FALSE, bold = FALSE, italic = TRUE) %>%
  add_header_above(c(" ", "Prediction supported?" = 4, " ")) %>%
  column_spec(1, width = "12cm") %>%
  column_spec(2:5, width = "1.2cm") %>%
  column_spec(6, width = "2.4cm") 
 # kableExtra::landscape()
```

Parentheses indicate that the prediction was supported by one but not all of the top full models (Table **5**). Dash symbols indicate that the response was not significant/ not represented in any of the top full models.
Asterisks indicate that the $Rt_{ARIMA}$ model yielded a different result: 
*$Rt_{ARIMA}$ had a difference in significance/ inclusion in top full models.
**$Rt_{ARIMA}$ model had a significant trend in the opposite direction of the $Rt$ model (if significant) or the prediction (if no significant trend in $Rt$ model).

>>>>

\blandscape
```{r Table 1, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
hypothesis_table <- read.csv("tables_figures/publication/table1_hypothesis_table.csv", stringsAsFactors = FALSE, check.names = FALSE)
kable(hypothesis_table, format = "latex", booktabs = TRUE, caption = "Table 1. Summary of hypotheses, corresponding specific predictions, and results.") %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 8.5, protect_latex = TRUE) %>%
  pack_rows("Tree size and microenvironment", 1, 3, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("Taller height makes trees less drought resistant.", 1, 1, latex_gap_space = "1em", colnum = 1, hline_before = FALSE, bold = FALSE, italic = TRUE) %>%
  pack_rows("Trees with more exposed crowns have lower drought resistance.", 2, 2, latex_gap_space = "1em", colnum = 1, hline_before = FALSE, bold = FALSE, italic = TRUE) %>%
  pack_rows("Small trees (lower root volume) in drier microhabitats have lower drought resistance.", 3, 3, latex_gap_space = "1em", colnum = 1, hline_before = FALSE, bold = FALSE, italic = TRUE) %>%
  pack_rows("Species traits", 4, 8, latex_gap_space = "1em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("Species' traits--particularly leaf hydraulic traits--predict drought reistance.", 4, 8, latex_gap_space = "1em", colnum = 1, hline_before = FALSE, bold = FALSE, italic = TRUE) %>%
  add_header_above(c(" ", "Prediction supported?" = 4, " ")) %>%
  column_spec(1, width = "12cm") %>%
  column_spec(2:5, width = "1.2cm") %>%
  column_spec(6, width = "2cm") 
 # kableExtra::landscape()
```

Parentheses indicate that the prediction was supported by one but not all of the top full models (Table S6). Dash symbols indicate that the response was not significant (Table S4)/ not represented in any of the top full models (Table S6).
Asterisks indicate that the $Rt_{ARIMA}$ models (Table S5, S7) yielded a different result: 
*$Rt_{ARIMA}$ had a difference in significance/ inclusion in top full models.
**$Rt_{ARIMA}$ model had a significant trend in the opposite direction of the $Rt$ model (if significant) or the prediction (if no significant trend in $Rt$ model).
